Code for Breast Cancer Pain Study

### 2020-07-24 manuscript_code_20200722.Rmd
tables

```{r,echo=FALSE,eval=FALSE}
table(final.data)
summary(final.data)
do.call("rbind",apply(final.data,2,get_summary))

get_summary = function(x) {
  tab = table(x)
  names(tab)

  summ = t(t(table(x)))
  names(summ)
}
x = final.data$Marital.status
t(t(table(final.data$Marital.status)))

## Try htmlTable
htmlTable(table.count,
          rgroup = c("","",gsub(pattern="[.]",replacement=" ",x=explvars[2:length(explvars)])),
          rnames = tablevars,
          n.rgroup = c(1,1,4,4,3,3,2,2,2,2,3),
          cgroup = c("Unadjusted","Adjusted"),
          n.cgroup = c(3,3))

## Distributions

@@

## Poverty

@@

# par(mfrow=c(3,3))
pdf(6,6,file=paste("Pain_poverty_legend.pdf"))
par(mar=c(4,4,2,2))
plot(x=c(0,1),y=c(0,1))
cbind(meandata$size,cex)

x = c(1,20,40,60,80)
y = c(1,1.5,2.5,4,6)
points(x=rep(0.4,length(x)),
       y=seq(0.8,0.4,length.out=length(x)),
       cex=y,lwd=2.5,col=brewer.pal(n=11,"BrBG")[9])
text(x=rep(0.55,length(x)),
     y=seq(0.8,0.4,length.out=length(x)),
     labels=x,cex=1.5)
dev.off()

@@

## Vacancy

@@

>>>>

## Figure 2

@@

### Poverty

@@

# par(mfrow=c(3,3))
pdf(6,6,file=paste("Pain_poverty_legend.pdf"))
par(mar=c(4,4,2,2))
plot(x=c(0,1),y=c(0,1),axes=F,cex=0,xlab=NA,ylab=NA)
# cbind(meandata$size,cex)

x = c(20,40,60,80)
y = c(1.5,2.5,4,6)
points(x=rep(0.4,length(x)),
       y=seq(0.8,0.4,length.out=length(x)),
       cex=y,lwd=2.5,col=brewer.pal(n=11,"BrBG")[9])
text(x=rep(0.55,length(x)),
     y=seq(0.8,0.4,length.out=length(x)),
     labels=x,cex=1.5)
text(x=0.5,y=0.95,
     labels="Number of patients",cex=1.5)
dev.off()

@@

### Vacancy

@@

# Analysis

## Figure 2

# Significance

```{r,echo=FALSE}
xlist = c("Poverty.f","marital.status.f","Primary.Payer.f2","Usual.Occupation.f2","race.f","stage.f","age.f","chemo.f","surgery.f")

x = xlist[1]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[2]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[3]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[4]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[5]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[6]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[7]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[8]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[9]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

```{r,echo=FALSE,eval=FALSE}
## Figure code - boxplot

x = "Poverty"
tmp = cdmd.pvt[,c("Pain","Poverty.f")]
colnames(tmp) = c("Pain",x)
tmp$Poverty = factor(tmp$Poverty)
tmp$Poverty = relevel(tmp$Poverty,"low")
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Marital.Status"
tmp <-
  cdmd.pvt %>%
  filter(marital.status.f2 %in% c("Married","Single")) %>%
  select("Pain","marital.status.f2")
colnames(tmp) = c("Pain",x)
class(tmp[,2])
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Primary.Payer"
tmp <-
  cdmd.pvt %>%
  filter(Primary.Payer.f2 %in% c("Insurance","Medicaid")) %>%
  select("Pain","Primary.Payer.f2")

colnames(tmp) = c("Pain",x)
class(tmp[,2])

base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))

ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Occupation"
tmp <-
  cdmd.pvt %>%
  filter(Usual.Occupation.f2 %in% c("Employed","Retired","Unemployed")) %>%
  select("Pain","Usual.Occupation.f2")

colnames(tmp) = c("Pain",x)
class(tmp[,2])

my_comparisons <- list( c("Employed", "Retired"), c("Retired", "Unemployed"), c("Employed", "Unemployed") )
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 15) +
  stat_compare_means(comparisons = my_comparisons, aes(label = ..p.signif..),hide.ns=T)

p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Race"
tmp <-
  cdmd.pvt %>%
  filter(race.f %in% c("White","Black")) %>%
  select("Pain","race.f")
colnames(tmp) = c("Pain",x)
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Age"
tmp <-
  cdmd.pvt %>%
  select("Pain","age.f")
colnames(tmp) = c("Pain",x)
tmp$Age[which(tmp$Age==0)] = "low"
tmp$Age[which(tmp$Age==1)] = "high"
tmp$Age = factor(tmp$Age)
tmp$Age = relevel(tmp$Age,"low")
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Surgery"
tmp <-
  cdmd.pvt %>%
  select("Pain","surgery.f")
colnames(tmp) = c("Pain",x)
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Chemo"
tmp <-
  cdmd.pvt %>%
  select("Pain","chemo.f")
colnames(tmp) = c("Pain",x)
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Stage"
tmp <-
  cdmd.pvt %>%
  select("Pain","stage.f")
colnames(tmp) = c("Pain",x)
my_comparisons <- list( c("1", "2"), c("2", "3"), c("1", "3") )
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 15) +
  stat_compare_means(comparisons = my_comparisons, aes(label = ..p.signif..),hide.ns=T)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

## Table 2
